\documentclass{article}
\usepackage{enumitem}

\title{ \line(1,0){415} \\ Formale Grundlagen der Informatik I -\\ Assignment 02 
\line(1,0){415}}
\author{Oliver Strassmann, 15-932-726}

\begin{document}
\maketitle

\section{The logic of Quantified Statements}
\begin{enumerate}[label=\alph*]
		\item
			\begin{enumerate}[label=\roman*]
				\item False, $\forall$x$\in$V: $\neg$ Hexagon(x)
				\item True, example: First row, second column.
				\item False, example: First row, first column "red circle", x $\in$V but $\neg$Square(x).
				\item False, counter-example: First row, last column, "green circle".
				\item Depends on definition of "the left" - not immidiately on the next left slot, but in the left yes.
				\item True.
			\end{enumerate}

		\item v and vi 
\end{enumerate}

\section{Number Theory and Proofs}
\begin{enumerate}[label=\alph*]
	\item m $\in$ $\mathbb{N}$, n = -m $\rightarrow$ this way we allways get 0, which is an integer.
	\item
		\begin{itemize}
			\item If we have two consecutive numbers, one number will allways be odd and the other one will be even.
			\item Every even number is a multiple of 2. 
			\item A product of two integers a$\cdot$b will always be divisible by a and b.
			\item Let's say a is our even number, if c = a$\cdot$b, then c is divisible by a, and a is divisible by 2 since its even, therefore c is also divisible by 2, meaning it's even.
	\end{itemize}
	\item  
		(7m + 1) : 7 =? integer \\*
		7m : 7 + 1 : 7 =? integer \\*
		7m : 7 = m, which is an integer \\*
		But: \\*
		1:7 != integer ! \\*
		$\rightarrow$ The statement leads to a contradiction, it is therefore false.
	\item 
		\begin{enumerate}[label=\roman*]
			\item a|b and a|c\\*
				(b + c) mod a =? 0 \\*
				(b mod a) + (c mod a) =? 0 \\*
				0 + 0 = 0
				$\rightarrow$The statement is true.
			\item
				c mod (a $\cdot$ b) =? 0 \\*
				(c mod a) $\cdot$ (c mod b) =? 0
				0 $\cdot$ 0 = 0 \\*
				$\rightarrow$The statement is true.
			\item n³= n * n * n; n is divisible by 2, therefore n³ is also divisible by 2, meaning it is even.
			\item True, example: a = 2, b = 3 \\*
				4 + 9 = 13, which is an odd integer
			\item
			\item
		\end{enumitem}
\end{enumerate}

\end{document}
